A Road Segment Prioritization Approach for Cycling Infrastructure

### 2023-05-01 README.tex
minor edit: equity literature

Other approaches have focused on characteristics of route segments as the basis of analysis to help prioritize investment in cycle infrastructure where it is most needed.
Grisé and El-Geneidy (2018) developed a multi-criteria approach, combined with estimated levels of usage, to highlight routes most in need of investment in Quebec City.
Wysling and Purves (2022) present a method that used open data from Paris to generate cycling suitability ratings based on `bicycle suitability multipliers' associated with different types of road across the city, to support more effective interventions.

None of the aforementioned studies explore the equity impacts of different network prioritization approaches.
The following section highlights the importance of considering (often unstated) ethical assumptions underlying network optimisation and prioritization approaches of the type outlined above.

@@

Our work builds on these community finding approaches by proposing a similar greedy network expansion algorithm for cycle network expansion \emph{within communities}.
We incorporate community finding methods for study area partitioning with weighted routing to avoid links that are stressful to cycle on.
In doing so, we propose an approach that ensures a better distribution investments across the study area while also accounting for motivators and deterrents to cycling.
We propose three sub-methods that address some of the limitations of previous studies.
These limitations include (a) an inherent bias when basing network design solely on existing cycling demand, (b) the proposal of routes that may not correspond to studies on cyclist preference and government policies, and (c) an insufficient consideration of the ethical principles underlying the analysis.
The current work addresses these limitations through the following organisation.
Section \ref{calculating-potential-cycling-demand} focuses on calculating potential cycling demand.
Section \ref{routing} focuses on routing the demand onto the road network while accounting for cyclist preferences and government priorities.
Section \ref{road-segment-prioritization} outlines a method for partitioning the study area based on a community finding algorithm and routed cycling demand.
It then introduces the network expansion algorithms, and compares an approach grounded in `egalitarianism' to one grounded in `utilitarianism'. ithms, and compares an approach grounded in
`egalitarianism' to one grounded in `utilitarianism'. As mentioned above, Manchester is used as a case study.
An overview of the steps involved is shown in Figure \ref{fig:methodflowchart}.

>>>>

Other approaches have focused on characteristics of route segments as the basis of analysis to help prioritize investment in cycle infrastructure where it is most needed.
Grisé and El-Geneidy (2018) developed a multi-criteria approach, combined with estimated levels of usage, to highlight routes most in need of investment in Quebec City.
Wysling and Purves (2022) present a method that used open data from Paris to generate cycling suitability ratings, based on `bicycle suitability multipliers' associated with different types of road across the city, to support more effective interventions.

With the exception of Grisé and El-Geneidy (2018), the aforementioned studies do not explore the equity impacts of different network prioritization approaches.
The following section highlights the importance of considering (often unstated) ethical assumptions underlying network optimization and prioritization approaches of the type outlined above.

@@

Our work builds on these community finding approaches by proposing a similar greedy network expansion algorithm for cycle network expansion \emph{within communities}.
We incorporate community finding methods for study area partitioning with weighted routing to avoid links that are stressful to cycle on.
In doing so, we propose an approach that ensures a better distribution investments across the study area while also accounting for motivators and deterrents to cycling.
We propose three sub-methods that address some of the limitations of previous studies.
These limitations include (a) an inherent bias when basing network design solely on existing cycling demand, (b) the proposal of routes that may not correspond to studies on cyclist preference and government policies, and (c) an insufficient consideration of the ethical principles underlying the analysis.
The current work addresses these limitations through the following organisation.
Section \ref{calculating-potential-cycling-demand} focuses on calculating potential cycling demand.
Section \ref{routing} focuses on routing the demand onto the road network while accounting for cyclist preferences and government priorities.
Section \ref{road-segment-prioritization} outlines a method for partitioning the study area based on a community finding algorithm and routed cycling demand.
It then introduces the network expansion algorithms, and compares an approach grounded in `egalitarianism' to one grounded in `utilitarianism'.
As mentioned above, Manchester is used as a case study.
An overview of the steps involved is shown in Figure \ref{fig:methodflowchart}.
